Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/failover.tex
Added VM failure figures for two different models

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Number of nodes failed},
		ylabel={chance that a VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		]
		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}

>>>>

\comments{\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Number of nodes failed},
		ylabel={chance that a VM is affected (\%) in VO},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		]
		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
                \legend{$VO_{C=5}$,$VO_{C=10}$,$VO_{C=20}$,$VO_{C=40}$,$VC_{C=100}$,$VC_{C=200}$,$VC_{C=400}$,$VC_{C=800}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}
